---
title: "Statistics Assignment"
author: "Anik Aslam"
date: "25/01/2020"
output: html_document
---

# STEP 1 - Data Collection
  
First Export data by running R command provided by professor in dataset.cvs,Importing same data here in variable mydata which contain word per minute (wmp) of 2 type keyboards 1) QWERTY and 2) AZERTY.As well 2 types of systems 1) Auto Correction and 2) no Help.

```{r}
mydata = read.csv(file.choose(),header = TRUE)
mydata 
```

# STEP 2 - Descriptive Statistics

### "Azerty" Keyboard Type
From Complete set of data, we filtered data of keyboard type AZERTY
```{r Keyboard type Azerty}
Azerty <- mydata[ which(mydata$keyboard=='azerty'), ]  # Data where keyboard=Azerty
Azerty
```


### Mean, Median and Standard Deviation Of AZERTY Keyboard Type
Calculating the Mean, Median and Standard Deviation of WMP of Keyboard type AZERTY 
```{r}
AzertyWmp <- Azerty[c(-1,-2,-3,-4)]  # Exluding each column except Wmp
Azer <- as.numeric(unlist(AzertyWmp))  #Converting list to Int
summary(Azer)     #Descriptive Statistics
sd(Azer)  #Standard deviation of wmp where keyboard is Azerty
```

### "Qwerty" Keyboard Type
From Complete set of data, we filtered data of keyboard type QWERTY
```{r Keyboard type Qwerty}
Qwerty <- mydata[ which(mydata$keyboard=='qwerty'), ]  # Data where keyboard=Qwerty
Qwerty
```

### Mean, Median and Standard Deviation of QWERTY keyboard Type
Calculating the Mean, Median and Standard Deviation of WMP of Keyboard type QWERTY 
```{r}
QwertyWmp <- Qwerty[c(-1,-2,-3,-4)]  # Exluding each column except Wmp
Qwer <- as.numeric(unlist(QwertyWmp))  #Converting list to Int
summary(Qwer)     #Descriptive Statistics
sd(Qwer)  #Standard deviation of wmp where keyboard is Qwerty
```

### "AutoCorrection" Keyboard System
From Complete set of data, we filtered data of keyboard System Autocorrection
```{r Keyboard system AutoCorrection}
Auto <- mydata[ which(mydata$system=='autocorrection'), ]  # Data where keyboard=Qwerty
Auto
```

### Mean, Median and Standard Deviation of AUTOCORRECTION Keyboard System
Calculating the Mean, Median and Standard Deviation of WMP of Keyboard system autocorrection 
```{r}
AutoWmp <- Auto[c(-1,-2,-3,-4)]
AutoWmpInt <- as.numeric(unlist(AutoWmp))
summary(AutoWmpInt)
sd(AutoWmpInt)
```

### "noHelp" Keyboard System
From Complete set of data, we filtered data of keyboard System NOHELP
```{r Keyboard system noHelp}
nohelp <- mydata[ which(mydata$system=='nohelp'), ]  # Data where keyboard=Qwerty
nohelp
```

### Mean. Median and Standard Deviation of keyboard system NOHELP
Calculating the Mean, Median and Standard Deviation of WMP of Keyboard system NOHELP 
```{r}
nohelpWmp <- nohelp[c(-1,-2,-3,-4)]
nohelpWmpInt <- as.numeric(unlist(nohelpWmp))
summary(nohelpWmpInt)
sd(nohelpWmpInt)
```

# STEP 3 - Plots

## Box Plot Of Both "Azerty" and "Qwerty" keyboard type
Showing the AZERTY and QWERTY Keyboard type using Box Plot
```{r}
#Boxplot of keyboard types AZERTY and QWERTY
boxplot(Azer,Qwer,xlab="Dataset for keyboard Type AZERTY AND QWERTY",ylab="WMP values")
axis(1, at = 1:2, labels = c("Azerty" , "Qwerty"))
```

## Box Plot Of Both "AUTO CORRECTION" and "NO HELP" keyboard system
Showing the AUTOCORRECTION and NOHELP Keyboard system using Box Plot
```{r}
#Boxplot of Nohelp and Auto-Correction of both keyboard Systems
boxplot(AutoWmpInt,nohelpWmpInt,xlab="Dataset for keyboard System AUTO AND NO HELP",ylab="WMP values")
axis(1, at = 1:2, labels = c("Auto Correction" , "No Help"))
```

## Q-Q plot Of Both "Azerty" and "Qwerty" keyboard type
Showing the data AZERTY and QWERTY Keyboard type using Q-Q PLOT
```{r}
#QQ plot of keyboard type AZERTY
qqnorm(Azer,xlab="Azerty",ylab ="WMP values")
qqline(Azer, col = "Red", lwd = 2)

#QQ plot of keyboard type QWERTY
qqnorm(Qwer,xlab="Qwerty",ylab ="WMP values")
qqline(Qwer, col = "steelblue", lwd = 2)
```

## Q-Q plot Of Both "AUTOCORRECTION" and "NOHELP" keyboard system
Showing the data AUTOCORRECTION and NOHELP Keyboard system using Q-Q PLOT
```{r}
#QQ plot of keyboard System Nohelp
qqnorm(nohelpWmpInt,xlab="No Help System",ylab ="WMP values")
qqline(nohelpWmpInt, col = "ORANGE", lwd = 2)

#QQ plot of keyboard System Autocorrection
qqnorm(AutoWmpInt,xlab="Auto System",ylab ="WMP values")
qqline(AutoWmpInt, col = "GREEN", lwd = 2)
```

### Observation from Box plot and Q-Q PLOT
Autocorrection keyboard system is faster than nohelp and AZERTY keyboard type is faster than QWERTY.Each data in Q-Q plot showing that they are near to normality.

# STEP 4

## Confidence Interval of keyboard type

Finding the CI of each keyboard type using t.test function with 95% confidence interval and calculating the mean difference of both keyboard type and for ploting it use the package named plotrix.
```{r}
#Confidence Interval of the mean WPM for each keyboard type
ciAzer <- t.test(Azer)$conf.int
ciQwer <- t.test(Qwer)$conf.int
cidiff <- t.test(Azer,Qwer)$conf.int
mAzer <- mean(Azer)
mQwer <- mean(Qwer)
plotrix::plotCI(c(1,2),c(mAzer,mQwer),ui=c(ciAzer[2],ciQwer[2]),li=c(ciAzer[1],ciQwer[1]),pch=19,xlab=NA,xaxt='n',xlim=c(.5,2.5),ylab="Azerty and Qwerty")
axis(1, at = 1:2, labels = c("Azerty" , "Qwerty"))
plotrix::plotCI(1, mAzer - mQwer, ui=cidiff[2], li=cidiff[1], pch=19, xlab="Diff b/w Azerty and Qwerty", xaxt='n', ylim=c(-1,15),ylab="")
segments(0, 0, 2,0, lty = 2)
```

### Conclusion for CI - KEYBOARD TYPE
Researcher hypothesis related to AZERTY AND QWERTY keyboard type is correct that typing with an AZERTY keyboard is faster than typing with a QWERTY keyboard (H2).Because The mean speed WPM of AZERTY is faster than QWERTY.

## Confidence Interval of keyboard system
Finding the CI of each keyboard system using t.test function with 95% confidence interval and calculating the mean difference of both keyboard system and for ploting it use the package named plotrix.

```{r}
#Confidence Interval of the mean WPM for each system
ciAuto <- t.test(AutoWmpInt)$conf.int
ciNo <- t.test(nohelpWmpInt)$conf.int
cidiffer <- t.test(AutoWmpInt,nohelpWmpInt)$conf.int
mAuto <- mean(AutoWmpInt)
mNo <- mean(nohelpWmpInt)
plotrix::plotCI(c(1,2),c(mAuto,mNo ),ui=c(ciAuto[2],ciNo[2]),li=c(ciAuto[1],ciNo[1]),pch=19,xlab=NA,xaxt='n',xlim=c(.5,2.5),ylab="Auto and No help")
axis(1, at = 1:2, labels = c("Auto" , "No help"))
plotrix::plotCI(1, mAuto - mNo, ui=cidiff[2], li=cidiff[1], pch=19, xlab="Diff b/w Auto and No help", xaxt='n', ylim=c(-1,15),ylab="")
segments(0, 0, 2,0, lty = 2)
```

### Conclusion for CI - KEYBOARD SYSTEM
Researcher hypothesis related to AUTOCORRECTION AND NOHELP keyboard system is correct that Typing with Auto-Correction is faster than typing with No Help (H1).Because The mean speed WPM of AUTOCORRECT is faster than NOHELP.

# Step 5 - Significance Tests

## For H1 - keyboard type Autocorrection and nohelp
Null hypothesis - Typing with Auto-Correction is same as typing with No Help 


Alternative hypothesis - Typing with Auto-Correction is faster than typing with No Help 

```{r}
t.test(Azer,Qwer)
```

### Conclusion for Significance test of H1
Hence it is viewable that P-value < 0.05 which means the null hypothesis is rejected and alternative hypothesis is correct.And the result of significant test is consistent with CI in step 4.

## For H2 - Keyboard system AZERTY and QWERTY
Null hypothesis - Typing with AZERTY is same as typing with QWERTY

Alternative hypothesis - Typing with an AZERTY keyboard is faster than typing with a QWERTY keyboard

```{r}
t.test(AutoWmpInt,nohelpWmpInt)
```

### Conclusion for significance test of H2
Hence it is viewable that P-value < 0.05 which means the null hypothesis is rejected and alternative hypothesis is correct.And the result of significant test is consistent with CI in step 4.

# Final Conclusion
The Descriptive Statistics(Mean, Median and Standard Deviation) are obtained by using R script for AZERTY , QWERTY , typing with Auto-Correction and No-help are calculated which are provided in the output.

1. The mean speed WPM of AZERTY is faster than QWERTY.

2. The mean speed WPM of Auto correction is faster than no help.

3. The Box-plot for keyboard systems and keyboard types are provided above.

4. The Q-Q plot of each system and type shows that data are near to normality.

5. The 95% CI for AZERTY and QWERTY is [0.5669267 8.2393233].

6. The 95% CI For Autocorrection and nohelp is [0.1656323 7.8906177]

7. The Significance test between the Autocorrection and nohelp is carried out     which shows that typing with Autocorrection is faster than nohelp.

8. The Significance test between AZERTY and QWERTY is carried out which shows     that typing with AZERTY is faster than QWERTY.
